---
title: "octave_connect"
author: "Zander Gordan"
date: "2/11/2021"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The R script provided here defines a [knitr engine](https://bookdown.org/yihui/rmarkdown-cookbook/custom-engine.html) that connects to [Octave](https://www.gnu.org/software/octave/) and passes it a command defining an array based on an R array.


```{r}
source("octave_connect.R")
example_array <- array(data = 1:16, dim = c(4,4))
example_array
```

```{octave_connect, r_array = "example_array"}
sum(example_array)
```

### Note

`octave_connect` feeds your code to Octave as a single string, with `;` separating the lines. This means that only a single `ans =` can be returned to knitr. If you place a `;` on the final line of your `octave_connect` chunk, nothing will be printed to the chunk output. However, if you are copying existing Octave code, do not worry about deleting any `;` at the end of intermediate lines, as that is not necessary.
