---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# octave.connect

<!-- badges: start -->
<!-- badges: end -->

This package defines a [knitr
engine](https://bookdown.org/yihui/rmarkdown-cookbook/custom-engine.html)
that connects to [Octave](https://www.gnu.org/software/octave/) and
passes it a command defining an array based on an R array.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zandergordan/octave.connect")
```
## Example

Here is a basic example of using the package. First, anywhere in your rmarkdown file (typically in the `setup`) chunk:

```{r setup}
library(octave.connect)
octave_connect("C:\\Users\\alexander.gordan\\AppData\\Local\\Programs\\GNU Octave\\Octave-6.1.0\\mingw64\\bin\\octave")
```

Then, define an R array:

```{r}
example_array <- array(data = 1:16, dim = c(4,4))
example_array
```

And now we can use an `octave_connect` chunk to do things with the array in Octave (to view the full syntax, look at `README.rmd` instead of the rendered `README.md`):


```{octave_connect, r_array = "example_array"}
sum(example_array)
```


